An efficient acyclic contact planner for multiped robots

### 2017-01-11 body/rbprm.tex
[rbprm]

In this Section we have thus presented a guide path planner for the geometric root of a robot. This planner is implemented as low a dimensional sampling based 
algorithm. Given start and goal configurations, it outputs a continuous path for the root of the robot, such that for any configuration in the path there exists a joint
configuration that results in static equilibrium.
%~ Thanks to these modifications, the problem of planning a \gls{contact reachable} path is reduced to a geometric collision-checking problem, of low dimension (6 for HyQ, 8 for HRP-2 that has 2 joints in the torso).
%~ By doing this we can solve the problem with a sampling-based approach, in \gls{interactive} computation times.

>>>>

In this Section we have thus presented a guide path planner for the geometric root of a robot. This planner is implemented as low a dimensional sampling based 
algorithm. Given start and goal configurations, it outputs a continuous path for the root of the robot. Thanks to the \textit{reachability condition}, we assume that any for any configuration in the path there exists a joint configuration that results in static equilibrium.
%~ Thanks to these modifications, the problem of planning a \gls{contact reachable} path is reduced to a geometric collision-checking problem, of low dimension (6 for HyQ, 8 for HRP-2 that has 2 joints in the torso).
%~ By doing this we can solve the problem with a sampling-based approach, in \gls{interactive} computation times.
